%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[References]{References}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[allowframebreaks]
\footnotesize
\begin{thebibliography}{10}
\bibitem{Huffman-Pless}Huffman W.C., Pless V.: Fundamentals of error-correcting codes, Cambridge University Press, Cambridge, 2010.
\bibitem{Ding-Ding}Ding K. Ding C.: A class of two-weight and three-weight codes and their applications in secret sharing. IEEE Trans. Inf. Theory {\bf61}(11), 5835-5842 (2015).
\bibitem{Luo-Fu-Vinck}Luo Y., Fu F.W., Vinck A.J.H., et al.: On constant-composition codes over $\mathbb{Z}_p$. IEEE Trans. Inform. Theory, {\bf49}(11), 3010-3016 (2003).
\bibitem{Ding-Wang}Ding C, Wang X.: A coding theory construction of new systematic authentication codes. Theor. Comput. Sci. {\bf330}(1), 81¨C99 (2005).
\bibitem{Lidl-Niederreiter}Lidl R., Niederreiter H., Cohn F.M.: Finite Fields. Cambridge University Press, Cambridge (1997).
\bibitem{Yang-Yao}Yang S., Yao Z.A.: Complete weight enumerators of a family of three-weight linear codes. Des. Codes Cryptogr., 1-12, 2016.
\bibitem{Li-Bae-Ahn}Li C., Bae S., Ahn J., et al.: Complete weight enumerators of some linear codes and their applications. Des. Codes Cryptogr., {\bf81}(1),153-168 (2016).
\bibitem{Li-Wang-Lin}Li F., Wang Q., Lin D.: A class of three-weight and five-weight linear codes. Discret. Appl. Math., 2017.
\bibitem{shi-liu-Sole1} Shi M., Liu Y., Sol$\acute{e}$ P.: Optimal two-weight codes from trace codes over $\mathbb{F}_2+ u\mathbb{F}_2$. IEEE Commun. Lett. {\bf20}(12), 2346-2349 (2016).
\bibitem{shi-liu-Sole2} Shi M., Luo Y., Sol$\acute{e}$ P.: Construction of one-Lee weight and two-Lee weight codes over $\mathbb{F}_p+ v\mathbb{F}_p$. J. Sys. Sci. Compl. {\bf30}(2), 484-493 (2017).
\bibitem{Liu-Maouche}Liu H., Maouche Y.: Several classes of trace codes with either optimal two weights or a few weights over $\mathbb{F}_{q}+u\mathbb{F}_{q}$.
  preprint arXiv:1703.04968 [cs.IT].
\bibitem{Guang-Zhang}Guang X. Zhang Z.: \emph{Linear Network Error Correction Coding}, Springer Press, New York, 2014.
\bibitem{Ahlswede-Cai-Li} Ahlswede R., Cai N., Li S.Y.R., et al.: Network information flow. IEEE Trans. Inform. Theory, {\bf46}(4), 1204-1216 (2000).
\bibitem{Yeung-Cai} Yeung R.W., Cai N.: Network error correction I: Basic concepts and upper bounds. Commun. Inform. Sys., {\bf6}(1), 19-35 (2006).
\bibitem{Cai-Yeung} Cai N., Yeung R.W.: Network error correction II: Lower bounds. Commun. Inform. Sys., {\bf6}(1), 37-54 (2006).
\bibitem{Zhang}Zhang Z.: Linear network error correction codes in packet networks. IEEE Trans. Inform. Theory, {\bf54}(1), 209-218 (2008).
\bibitem{Yang-Yeung-Ngai} Yang S., Yeung R.W., Ngai C.K.: Refined coding bounds and code constructions for coherent network error correction. IEEE Trans. Inform. Theory, {\bf57}(3), 1409-1424 (2011).
\bibitem{Guang-Fu-Zhang} Guang X., Fu F.W., Zhang Z.: Construction of network error correction codes in packet networks. IEEE Trans. Inform. Theory, {\bf59}(2), 1030-1047 (2013).
\bibitem{Guang-Fu-Zhang1} Guang X., Fu F.W., Zhang Z.: Variable-Rate Linear Network Error Correction MDS Codes. IEEE Trans. Inform. Theory, {\bf62}(6), 3147-3164 (2016).
\end{thebibliography}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
